Plots

### 2025-06-23 manuscript/manuscript.tex
Add range to perf plots

@@

\textbf{Conclusion:} All models performed similarly at the population level, while GPT-3.5/4 and InSilicoVA performed better for some CODs at the individual level. GPT models made improvements over InSilicoVA and InterVA-5. Our research lays the foundation for future work in computer assisted VA, where physicians utilize alternative COD assignments from computer models to help reduce ill-defined codes and physician disagreement.
}

@@

Of all 6939 records, GPT-4 (0.61 PCCC) had the highest individual performance followed by GPT-3.5 (0.56 PCCC), InSilicoVA (0.44 PCCC), and InterVA-5 (0.44 PCCC) (Figure \ref{fig-pccc-csmf}). GPT-3.5 and GPT-4 had improvements ranging from 0.14-0.18 PCCC over InSilicoVA and InterVA-5, while GPT-4 slightly improved over GPT-3.5 by 0.05 PCCC. Population level performances were similar for all models (0.74-0.79 CSMF). Figure \ref{fig-pccc} shows the PCCC performance across three age groups (adult, child, and neonate). GPT-4 had the best individual performance for adult and neonatal records (0.64 and 0.58 PCCC), while GPT-3.5 had the best performance for child records (0.54 PCCC) with GPT-4 performing slightly worse (0.51 PCCC). InSilicoVA and InterVA-5 performed the worse for adult and child records ($\leq$0.5 PCCC), while GPT-3.5 performed the worse for neonatal records (0.42 PCCC). Across ages, all models followed a similar pattern in individual performance (Figure \ref{fig-pccc-age}). PCCC trended upwards for 1 month to 14 years ($\sim$0.1-0.75), and downwards for ages 15 to 69 years ($\sim$0.7-0.35). The highest and lowest performances were observed for ages 12-29 years ($\sim$0.4-0.7) and 1-11 months ($\sim$0.1-0.35) respectively. Performances varied more across models for ages 0 days to 5 years, while varying less from 5 to 69 years between GPT-3.5 and GPT-4, and between InSilicoVA and InterVA-5.

@@

At the population level, overall performances for all models were similar to physicians (0.74-0.79 CSMF), indicating potential for adequately estimating COD distributions for large populations. Although all models did not perform well for all records at the individual level (0.44-0.61 PCCC), several models performed well for certain CODs (0-0.99 PCCC). For most CODs, GPT-3.5/GPT-4 performed better than InSilicoVA/InterVA-5 (top PCCC for 15 of 17, 7 of 8, and 4 of 5 adult, child, and neonatal CODs respectively), while InSilicoVA performed better for particular CODs (road and transport injuries, tuberculosis, pneumonia, and neonatal infections with 0.84, 0.71, 0.78, and 0.86 PCCC respectively). For CODs with high performance (e.g. GPT-3.5/4 with 0.91-0.99 PCCC for maternal conditions, chronic respiratory disease, diabetes melitus, and cancers, InSilicoVA with 0.84 and 0.86 PCCC for road and transport injuries, and neonatal infections), the results suggest that GPT-3.5/4 and InSilicoVA may assign CODs that are very similar to physicians. Thus, it may be beneficial to evaluate performance at the COD level, and apply a combination of models that perform well in comparison to physicians for each COD. For example, different models perform well for various leading CODs as seen in Table \ref{tab-leadcod} \citep{worldhealthorganizationWorldHealthStatistics2024,worldhealthorganizationCausespecificMortality2000}.

\begin{table}[h]
    \caption{Leading causes globally in 2021 and most relevant models.}\label{tab-leadcod}%
    \begin{tabular}{@{}llll@{}}
    \toprule
    \makecell{Leading Causes of Death\\($\sim$53\% of 68M deaths)\footnotemark[1]} & \makecell{Deaths\\(\% of 68M)\footnotemark[2]} & \makecell{Best\\Model(s)} & \makecell{PCCC} \\
    \midrule

    Ischaemic heart disease & 9M (13\%) & GPT-4 & 0.65 (n=168)\\ 
    Stroke & 7M (10\%) & GPT-4 & 0.77 (n=331)\\
    Cancers & 4.3M (4\%) & GPT-4 & 0.91 (n=49)\\
    Lower respiratory infections & 2.4M (3\%) & GPT-3.5/4 & 0.78 (n=180)\footnotemark[3]\\
    Diabetes mellitus & 1.6M (2\%) & GPT-3.5 & 0.92 (n=27)\\
    Tuberculosis & 1.4M (2\%) & InSilicoVA & 0.71 (n=171)\\
    Hypertensive heart disease & 1.4M (2\%) & GPT-4 & 0.78 (n=107)\footnotemark[4]\\
    Cirrhosis of the liver & 1.3M (2\%) & GPT-3.5 & 0.78 (n=128)\footnotemark[5]\\ 
    Diarrhoeal diseases & 1.2M (2\%) & GPT-4 & 0.68 (n=205)\\ 
    Road injury & 1,183 (2\%) & InSilicoVA & 0.84 (n=357)\\
    Preterm birth complications & 0.9M (1\%) & GPT-4 & 0.71 (n=73)\\
    Falls & 0.7M (1\%) & GPT-4 & 0.89 (n=492)\footnotemark[6]\\

    \botrule
    \end{tabular}
    \footnotetext[1]{COVID-19, kidney disease, alzheimer disease, other dementias, and self-harm were excluded as a relevant CGHR-10 code was not present. Trachea, bronchus, lung, colon, rectum, stomache, and breast cancers were generalized into cancers.}
    \footnotetext[2]{Percentage of $\sim$68 Million (M) deaths globally. Numbers are rounded.}
    \footnotetext[3]{Mean of chronic and acute respiratory infections.}
    \footnotetext[4]{Derived from other cardiovascular diseases.}
    \footnotetext[5]{Derived from liver and alcohol related diseases.}
    \footnotetext[6]{Mean of adult and child injuries.}
\end{table}

@@

The datasets supporting the conclusions of this article are included within the article (and its additional files), at \url{https://openmortality.org} (available upon request) and at \url{https://github.com/cghr-toronto/healsl-gpt-paper}. Verbal Autopsy (VA) and narrative data by age group and survey rounds 1 and 2 available at \url{https://openmortality.org/dataset/heal-sl}. Cause of death code mappings to convert between ICD-10, WVA-2016, and CGHR-10 codes available at \url{https://openmortality.org/dataset/icd}. Model evaluation result files at \url{https://github.com/cghr-toronto/healsl-gpt-paper/tree/main/data}.

>>>>

\author[1]{\fnm{Catherine} \sur{Meh}}\email{catherine.meh@unityhealth.to}

@@

\textbf{Conclusion:} All models performed similarly at the population level, while GPT-3.5/4 and InSilicoVA performed better for several CODs at the individual level. GPT models made improvements over InSilicoVA and InterVA-5 models. Our research lays the foundation for future work in computer assisted VA, where physicians utilize alternative COD assignments from computer models to help reduce ill-defined codes and physician disagreement.
}

@@

Of all 6939 records, GPT-4 (0.61 PCCC) had the highest individual performance followed by GPT-3.5 (0.56 PCCC), InSilicoVA (0.44 PCCC), and InterVA-5 (0.44 PCCC) (Figure \ref{fig-pccc-csmf}). GPT-3.5 and GPT-4 had improvements ranging from 0.14-0.18 PCCC over InSilicoVA and InterVA-5, while GPT-4 slightly improved over GPT-3.5 by 0.05 PCCC. Population level performances were similar for all models (0.74-0.79 CSMF). Figure \ref{fig-pccc} shows the PCCC performance across three age groups (adult, child, and neonate). GPT-4 had the best individual performance for adult and neonatal records (0.64 and 0.58 PCCC), while GPT-3.5 had the best performance for child records (0.54 PCCC) with GPT-4 performing slightly worse (0.51 PCCC). InSilicoVA and InterVA-5 performed the worse for adult and child records ($\leq$0.5 PCCC), while GPT-3.5 performed the worse for neonatal records (0.42 PCCC). Across ages, all models followed a similar pattern in individual performance (Figure \ref{fig-pccc-age}), where PCCC trended upwards for 1 month to 14 years ($\sim$0.1-0.75), and downwards for ages 15 to 69 years ($\sim$0.7-0.35). The highest and lowest performances were observed for ages 12-29 years ($\sim$0.4-0.7) and 1-11 months ($\sim$0.1-0.35) respectively.

@@

At the population level, overall performances for all models were similar to physicians (0.74-0.79 CSMF), indicating potential for adequately estimating COD distributions for large populations. Although all models did not perform well for all records at the individual level (0.44-0.61 PCCC), several models performed well for certain CODs (0-0.99 PCCC). For most CODs, GPT-3.5/GPT-4 performed better than InSilicoVA/InterVA-5 (top PCCC for 15 of 17, 7 of 8, and 4 of 5 adult, child, and neonatal CODs respectively), while InSilicoVA performed better for particular CODs (road and transport injuries, tuberculosis, pneumonia, and neonatal infections with 0.84, 0.71, 0.78, and 0.86 PCCC respectively). For CODs with high performance (e.g. GPT-3.5/4 with 0.91-0.99 PCCC for maternal conditions, chronic respiratory disease, diabetes melitus, and cancers, InSilicoVA with 0.84 and 0.86 PCCC for road and transport injuries, and neonatal infections), the results suggest that GPT-3.5/4 and InSilicoVA may assign CODs that are very similar to physicians. Thus, it may be beneficial to evaluate performance at the COD level, and apply a combination of models that perform well in comparison to physicians for each COD. For example, different models perform well for various leading CODs as seen in Table \ref{tab-leadcod} \citep{carshon-marshChildMaternalAdult2022,ansumanaReportCausesDeath2023}.

\begin{table}[h]
    \caption{Top ten leading causes of death for Sierra Leone in 2023 and most relevant models.}\label{tab-leadcod}%
    \begin{tabular}{@{}llll@{}}
    \toprule
    \makecell{Top 10 Leading Cause of Death\footnotemark[1]\\($\sim$71\% of $\sim$76K deaths)} & \makecell{Deaths\\(\% of 76K)\footnotemark[2]} & \makecell{Best\\Model(s)} & \makecell{PCCC\footnotemark[3]} \\
    \midrule

    Malaria & 16,075 (21\%) & GPT-3.5/4 & 0.46 (n=2181) \\
    Infections & 11,777 (16\%) & GPT-3.5/4/InSilicoVA & 0.55 (n=1155) \\
    Ischaemic heart and other vascular & 5,747 (8\%) & GPT-4 & 0.65 (n=168) \\
    Diarrhoea & 4,285 (6\%) & GPT-4 & 0.79 (n=380) \\
    Stroke & 4,262 (6\%) & GPT-4 & 0.77 (n=331) \\
    Pneumonia & 3,074 (4\%) & GPT-4/InSilicoVA & 0.7 (n=186) \\
    Birth asphyxia and birth trauma & 2,431 (3\%) & GPT-4 & 0.63 (n=103) \\
    Tuberculosis & 2,399 (3\%) & InSilicoVA & 0.71 (n=171) \\
    Low birth weight/preterm & 1,570 (2\%) & GPT-4 & 0.71 (n=103) \\
    Asthma and chronic respiratory & 1,551 (2\%) & GPT-3 & 0.94 (n=75)\\

    \botrule
    \end{tabular}
    \footnotetext[1]{Other infections and severe systemic/localized infections were generalized into infections. Appendix, hernia, intestinal and Peptic ulcer/gastroesophageal causes did not have comparable CGHR-10 codes and were omitted.}
    \footnotetext[2]{Percentage of $\sim$76 Thousand (K) total deaths \citep{ansumanaReportCausesDeath2023}. Numbers are rounded.}
    \footnotetext[3]{Adult, child, and neonate mean PCCC and summed n records if available.}
\end{table}

@@

The datasets supporting the conclusions of this article are included within the article (and its additional files), at \url{https://openmortality.org} (available upon request). Verbal Autopsy (VA) and narrative data by age group and survey rounds 1 and 2 available at \url{https://openmortality.org/dataset/heal-sl}. Cause of death code mappings to convert between ICD-10, WVA-2016, and CGHR-10 codes available at \url{https://openmortality.org/dataset/icd}.

### 2025-06-23 src/plots.Rmd
Add range to perf plots

# Plot performance of models using lines and points
plot_perf <- function(
        df_long,
        f = calc_pccc,
        group = "cod_name",
        color = "model_name",
        text_scale = 1,
        title = NULL,
        title_size = 10,
        x_title = NULL,
        y_title = NULL,
        text_mid_size = 2.25 * text_scale,
        text_mid_vjust = 2.5,
        text_start_size = 3 * text_scale,
        text_end_size = 4 * text_scale,
        text_hjust = 0.2,
        add_min_points = F,
        add_max_points = F,
        mid_points_size = 4,
        min_points_size = 4,
        max_points_size = 4,
        x_limits = c(0, 1),
        x_breaks = seq(0, 1, by = 0.1),
        x_expand = expansion(add = 0.2),
        x_color_labels = c(
            "G3" = "GPT-3.5 (G3)",
            "G4" = "GPT-4 (G4)",
            "ISV" = "InSilicoVA (ISV)",
            "I5" = "InterVA-5 (I5)"
        ),
        x_title_size = 9 * text_scale,
        y_title_size = 9 * text_scale,
        x_text_size = 8 * text_scale,
        y_text_size = 9 * text_scale,
        sort_group = T,
        legend_position = "bottom",
        legend_title = element_blank(),
        legend_margin = margin(c(-8, -2, -2, -2)),
        ...
    ) {

@@

    # Add min and max values for each group
    df_ends <- df_plot %>%
        group_by(.data[[group]]) %>%
        summarize(
            min_metric = min(metric),
            max_metric = max(metric),
            model_min = model_name[which.min(metric)],
            model_max = model_name[which.max(metric)]
        ) %>%
        arrange(max_metric)

@@

    # Plot metric for each model
    out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
        geom_segment( # min max lines
            data = df_ends,
            aes(
                x = min_metric,
                xend = max_metric,
                y = .data[[group]],
                yend = .data[[group]]
            ),
            linewidth = 0.75
        ) +
        geom_point( # points
            shape = 21,
            color = "black",
            aes(fill = .data[[color]]),
            size = mid_points_size
        ) +
        geom_text( # min model text
            data = df_ends,
            aes(
                x = min_metric,
                y = .data[[group]],
                label = paste0(model_min, ": ", round(min_metric, 2))
            ),
            hjust = 1 + text_hjust,
            vjust = 0.5,
            size = text_start_size
        ) +
        geom_text( # max model text
            data = df_ends,
            aes(
                x = max_metric,
                y = .data[[group]],
                label = paste0(model_max, ": ", round(max_metric, 2))
            ),
            hjust = 0 - text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text_repel( # mid model text
            data = df_mids,
            aes(label = model_label),
            color = "gray60",
            vjust = text_mid_vjust,
            max.overlaps = Inf,
            size = text_mid_size
        ) +
        scale_fill_discrete(
            labels = x_color_labels
        ) +
        scale_x_continuous(
            limits = x_limits,
            breaks = x_breaks,
            expand = x_expand
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            legend.position = legend_position,
            legend.title = legend_title,
            legend.margin = legend_margin,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )

@@

# Rename COD names
df <- df %>%
    mutate(across(
        c(
            physician_cghr10,
            gpt3_cghr10,
            gpt4_cghr10,
            insilicova_cghr10,
            interva5_cghr10
        ),
        ~ case_when(
            .x == "Maternal conditions" ~ "Maternal",
            .x == "Acute respiratory infections" ~ "Pneumonia",
            .x == "Neonatal infections" ~ "Infections",
            .default = .x
        ) %>%
            str_replace_all(" diseases| disease", "")
    ))

@@

# Plot data
fig_pccc_csmf <- ggplot(
    df_plot,
    aes(
        x = metric_value,
        y = model_name,
        fill = metric
    )
) +
    geom_bar(
        stat = "identity",
        position = position_dodge(),
        color = "black",
        width = 0.7
    ) +
    geom_text(
        data = df_plot,
        aes(
            label = round(metric_value, 2)
        ),
        position = position_dodge(width = 0.7),
        color = "black",
        fill = "white",
        size = 4.5,
        label.r = unit(0, "pt"),
        vjust = 0.5,
        hjust = -0.25
    ) +
    scale_x_continuous(
        limits = c(0, 1),
        breaks = seq(0, 1, 0.1)
    ) +
    labs(
        title = NULL,
        x = NULL,
        y = NULL
    ) +
    theme_minimal() +
    theme(
        # panel.border = element_rect(
        #     color = "black",
        #     fill = NA,
        #     linewidth = 0.75
        # ),
        legend.position = c(.875, .45),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 10),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12)
    )

@@

# Plot perf for pccc by age groups
fig_pccc <- plot_perf(
    df_long %>%
        mutate(
            age_label = case_when(
                age_name == "Adult"
                    ~ paste0(age_name, "\n12+ Years\n(n=", n_adult, ")"),
                age_name == "Child"
                    ~ paste0(age_name, "\n28 Days to 11 Years\n(n=", n_child, ")"),
                age_name == "Neonate"
                    ~ paste0(age_name, "\n<28 Days\n(n=", n_neo, ")"),
                .default = age_name
            ) %>%
                factor(., levels = unique(.) %>% sort %>% rev)
        ),
    calc_pccc,
    group = "age_label",
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    text_mid_vjust = 2,
    sort_group = F,
    x_limits = c(0.2, 0.8),
    legend_margin = margin(-8, -2, -2, -2),
    x_expand = waiver(),
    text_scale = 1.25
)

@@

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
    x_title =  "Partial Chance Corrected Concordance (PCCC)",
    text_mid_vjust = 2,
    text_scale = 1.25
)

# Save plot
ggsave(
    "../manuscript/fig-pccc-cod-adult.pdf",
    fig_pccc_cod_adult,
    width = 170,
    height = 250,
    units = "mm",
    dpi = 300
)

@@

# Plot child perf for pccc by cod
fig_pccc_cod_child <- plot_perf(
    df_long %>% filter(age == "child"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    text_mid_vjust = 4,
    text_scale = 1.15
)

>>>>

# Plot performance of models using lines and points
plot_perf <- function(
        df_long,
        f = calc_pccc,
        group = "cod_name",
        color = "model_name",
        text_scale = 1,
        title = NULL,
        title_size = 10,
        x_title = "Partial Chance Corrected Concordance (PCCC) / R = PCCC Range",
        y_title = NULL,
        text_mid_size = 2.25 * text_scale,
        text_mid_vjust = 2.5,
        text_start_size = 2.75 * text_scale,
        text_end_size = 3.5 * text_scale,
        text_hjust = 0.2,
        add_min_points = F,
        add_max_points = F,
        mid_points_size = 4,
        min_points_size = 4,
        max_points_size = 4,
        x_limits = c(0, 1.15),
        x_breaks = seq(0, 1, by = 0.1),
        x_expand = expansion(add = 0.2),
        x_color_labels = c(
            "G3" = "GPT-3.5 (G3)",
            "G4" = "GPT-4 (G4)",
            "ISV" = "InSilicoVA (ISV)",
            "I5" = "InterVA-5 (I5)"
        ),
        x_title_size = 9 * text_scale,
        y_title_size = 9 * text_scale,
        x_text_size = 8 * text_scale,
        y_text_size = 9 * text_scale,
        sort_group = T,
        legend_position = "bottom",
        legend_title = element_blank(),
        legend_margin = margin(c(-8, -2, -2, -2)),
        ...
    ) {

@@

    # Add min and max values for each group
    df_ends <- df_plot %>%
        group_by(.data[[group]]) %>%
        summarize(
            min_metric = min(metric),
            max_metric = max(metric),
            model_min = model_name[which.min(metric)],
            model_max = model_name[which.max(metric)],
            group_range = diff(range(metric))
        ) %>%
        arrange(max_metric)

@@

    # Plot metric for each model
    out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
        geom_segment( # min max lines
            data = df_ends,
            aes(
                x = min_metric,
                xend = max_metric,
                y = .data[[group]],
                yend = .data[[group]]
            ),
            linewidth = 0.75
        ) +
        geom_point( # points
            shape = 21,
            color = "black",
            aes(fill = .data[[color]]),
            size = mid_points_size
        ) +
        geom_text( # min model text
            data = df_ends,
            aes(
                x = min_metric,
                y = .data[[group]],
                label = paste0(model_min, ": ", round(min_metric, 2))
            ),
            hjust = 1 + text_hjust,
            vjust = 0.5,
            size = text_start_size
        ) +
        geom_text( # max model text
            data = df_ends,
            aes(
                x = max_metric,
                y = .data[[group]],
                label = paste0(
                    model_max, ": ", round(max_metric, 2),
                    " (R=", round(group_range, 2), ")"
                )
            ),
            hjust = 0 - text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text_repel( # mid model text
            data = df_mids,
            aes(label = model_label),
            color = "gray60",
            vjust = text_mid_vjust,
            max.overlaps = Inf,
            size = text_mid_size
        ) +
        scale_fill_discrete(
            labels = x_color_labels
        ) +
        scale_x_continuous(
            limits = x_limits,
            breaks = x_breaks,
            expand = x_expand
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            legend.position = legend_position,
            legend.title = legend_title,
            legend.margin = legend_margin,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )

@@

# Rename COD names
df <- df %>%
    mutate(across(
        c(
            physician_cghr10,
            gpt3_cghr10,
            gpt4_cghr10,
            insilicova_cghr10,
            interva5_cghr10
        ),
        ~ case_when(
            .x == "Maternal conditions" ~ "Maternal",
            .x == "Acute respiratory infections" ~ "Pneumonia",
            .x == "Neonatal infections" ~ "Infections",
            .x == "Road and transport injuries" ~ "Road/transport injuries",
            .x == "Liver and alcohol related diseases" ~ "Liver/alcohol",
            .x == "Birth asphyxia and trauma" ~ "Birth asphyxia/trauma",
            .default = .x
        ) %>%
            str_replace_all(" diseases| disease", "")
    ))

@@

# Plot data
fig_pccc_csmf <- ggplot(
    df_plot,
    aes(
        x = metric_value,
        y = model_name,
        fill = metric
    )
) +
    geom_bar(
        stat = "identity",
        position = position_dodge(),
        color = "black",
        width = 0.7
    ) +
    geom_text(
        data = df_plot,
        aes(
            label = round(metric_value, 2)
        ),
        position = position_dodge(width = 0.7),
        color = "black",
        fill = "white",
        size = 4.5,
        label.r = unit(0, "pt"),
        vjust = 0.5,
        hjust = -0.25
    ) +
    scale_x_continuous(
        limits = c(0, 1),
        breaks = seq(0, 1, 0.1)
    ) +
    labs(
        title = NULL,
        x = NULL,
        y = NULL
    ) +
    guides(
        fill = guide_legend(reverse = TRUE)
    ) +
    theme_minimal() +
    theme(
        legend.position = c(.875, .45),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 10),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12)
    )

@@

# Plot perf for pccc by age groups
fig_pccc <- plot_perf(
    df_long %>%
        mutate(
            age_label = case_when(
                age_name == "Adult"
                    ~ paste0(age_name, "\n12+ Years\n(n=", n_adult, ")"),
                age_name == "Child"
                    ~ paste0(age_name, "\n28 Days to 11 Years\n(n=", n_child, ")"),
                age_name == "Neonate"
                    ~ paste0(age_name, "\n<28 Days\n(n=", n_neo, ")"),
                .default = age_name
            ) %>%
                factor(., levels = unique(.) %>% sort %>% rev)
        ),
    calc_pccc,
    group = "age_label",
    text_mid_vjust = 2,
    sort_group = F,
    x_limits = c(0.2, 0.9),
    legend_margin = margin(-8, -2, -2, -2),
    x_expand = waiver(),
    text_scale = 1.25
)

@@

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
    text_mid_vjust = 2,
    text_scale = 1
)

# Save plot
ggsave(
    "../manuscript/fig-pccc-cod-adult.pdf",
    fig_pccc_cod_adult,
    width = 170, # min 170 mm full / 85 mm half
    height = 225, # max 225 mm
    units = "mm",
    dpi = 300
)

@@

# Plot child perf for pccc by cod
fig_pccc_cod_child <- plot_perf(
    df_long %>% filter(age == "child"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
    text_mid_vjust = 4,
    text_scale = 1
)
